Novel crystallization pathway\\and formation of ``colloidal rain'' during viscoelastic phase separation

### 2015-10-05 crystal-gel/crystal_gel_letter.tex
Fixed the equation for the radius of gyration.

%\documentclass[twocolumn,superscriptaddress,showpacs,preprintnumbers,amsmath,amssymb,prl]{revtex4-1}
\documentclass[twocolumn,showpacs,amsmath,amssymb,pre,superscriptaddress]{revtex4}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}% Include figure files
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{comment}
\usepackage{siunitx}
%\usepackage{dcolumn}% Align table columns on decimal point
%\usepackage{bm}% bold math

@@

\begin{figure*}[!t]
 \centering
 \includegraphics{./fig/phase_separation.pdf}
 \caption{{\bf Different routes of viscoelastic phase separation.}
 \textbf{a,} Phase diagram. Dashed lines are fluid-solid equilibrium coexistence boundaries. The continuous line is the gas side of the metastable gas-liquid spinodal region with the black diamond marking the critical point. The other symbols are the experimental points, consistently used in all panels.
 \textbf{b,} Radius of gyration ($R_g$) as a function of cluster size ($s$) for all state points at percolation. The
 gray line represents the fractal dimension of the random gelation universality class.
 \textbf{c,} Structure factors for the late stages of the gelation process. The gray and black lines represents respectively random gelation and compact fractal dimensions.
 \textbf{d,} Local volume fraction around a colloidal particle, as a function of the number of nearest neighbours of the particle \textcolor{blue}{at late stage?}. Horizontal lines stress the value at 12 neighbours.
 }
 \label{fig:phase_separation}
\end{figure*}

@@

\paragraph*{Experimental}
We use \textsc{pmma} (poly(methyl methacrylate)) colloids sterically stabilized with methacryloxypropyl terminated \textsc{pdms}(poly(dimethyl siloxane)) and fluorescently labelled with rhodamine isothiocyanate chemically bonded to the \textsc{pmma}. We disperse the particles in refractive index and density matching mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane (Sigma-Aldrich).

To induce short-ranged depletion attraction, we use polystyrene (TOSOH) of molecular weight \SI{3.8}{\mega\dalton} as non-adsorbing polymer. Experiments are conducted at \SI{27}{\celsius}, some \SI{80}{\celsius} above the theta temperature in this solvents mixture~\cite{Royall2007}. A Flory scaling of the measurements of~\cite{lu2008gelation} yields a radius of gyration $R_g=\SI{76}{\nano\metre}$.

In the absence of salt, the Debye length is expected to reach several \si{\micro\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion. We confirm that colloids never come close enough to feel the short-ranged attraction. Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \SI{100}{\nano\metre}, practically discarding the repulsion.

The data are collected on a Leica SP5 confocal microscope, using \SI{532}{\nano\metre} laser excitation. We assess that the size distribution of our particle is Gaussian with a polydispersity below 5\% via direct confocal measurements~\cite{Leocmach2013}. The mean diameter is $\sigma=\SI{2.1}{\micro\metre}$ XXX to be checked XXX yielding a size ratio $q_R=2R_g/\sigma=0.07$. The Brownian time is $\tau_B \approx \SI{4.5}{\second}$. To be able to follow individual trajectories, we perform a 3D scan every \SI{10}{\second} at early time and every \SI{30}{\second} later.

@@

\paragraph*{Structural analysis}
To account for imprecision in particle localisation close to contact, we consider two particles bonded if their center-to-center distance is within $\SI{2.3}{\micro\metre}>\sigma+2R_g$.

To detect percolation, two different methods have been employed. In the first one we detect percolation
by looking at which frame the cluster size distribution has a more extended power-law decay. In the second technique,
we simply measure the spatial extent of the largest cluster and consider it percolating when it is comparable to the
size of the field of view of the microscope. Both methods lead to essentially identical percolation time for each state point.

@@

\section{Future things to do}
Is the absence of network restructuring that is preventing crystallization?

>>>>

%\documentclass[twocolumn,superscriptaddress,showpacs,preprintnumbers,amsmath,amssymb,prl]{revtex4-1}
\documentclass[twocolumn,showpacs,amsmath,amssymb,pre,superscriptaddress]{revtex4}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}% Include figure files
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{comment}
%\usepackage{siunitx}
%\usepackage{dcolumn}% Align table columns on decimal point
%\usepackage{bm}% bold math

@@

\begin{figure*}[!t]
 \centering
 \includegraphics{./fig/phase_separation.pdf}
 \caption{{\bf Different routes of viscoelastic phase separation.}
 \textbf{a,} Phase diagram. Dashed lines are fluid-solid equilibrium coexistence boundaries. The continuous line is the gas side of the metastable gas-liquid spinodal region with the black diamond marking the critical point. The other symbols are the experimental points, consistently used in all panels.
 \textbf{b,} Radius of gyration ($R_g$) as a function of cluster size ($s$) for all state points at percolation. The
 gray line represents the fractal dimension of the random gelation universality class.
 \textbf{c,} Structure factors for the late stages of the gelation process. The gray and black lines represents respectively random gelation and compact fractal dimensions.
 Inset: same data in linear scales, shifted vertically for clarity.
 \textbf{d,} Local volume fraction around a colloidal particle, as a function of the number of nearest neighbours of the particle \textcolor{blue}{at late stage?}. Horizontal lines stress the value at 12 neighbours.
 }
 \label{fig:phase_separation}
\end{figure*}

@@

% \paragraph*{Experimental}
% We use \textsc{pmma} (poly(methyl methacrylate)) colloids sterically stabilized with methacryloxypropyl terminated \textsc{pdms}(poly(dimethyl siloxane)) and fluorescently labelled with rhodamine isothiocyanate chemically bonded to the \textsc{pmma}. We disperse the particles in refractive index and density matching mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane (Sigma-Aldrich).
% 
% To induce short-ranged depletion attraction, we use polystyrene (TOSOH) of molecular weight \SI{3.8}{\mega\dalton} as non-adsorbing polymer. Experiments are conducted at \SI{27}{\celsius}, some \SI{80}{\celsius} above the theta temperature in this solvents mixture~\cite{Royall2007}. A Flory scaling of the measurements of~\cite{lu2008gelation} yields a radius of gyration $R_g=\SI{76}{\nano\metre}$.
% 
% In the absence of salt, the Debye length is expected to reach several \si{\micro\metre} and the (weakly) charged colloids experience a long range electrostatic repulsion. We confirm that colloids never come close enough to feel the short-ranged attraction. Screening by tetrabutylammonium bromide (Fluka) at saturated concentration brings down the Debye length to about \SI{100}{\nano\metre}, practically discarding the repulsion.
% 
% The data are collected on a Leica SP5 confocal microscope, using \SI{532}{\nano\metre} laser excitation. We assess that the size distribution of our particle is Gaussian with a polydispersity below 5\% via direct confocal measurements~\cite{Leocmach2013}. The mean diameter is $\sigma=\SI{2.1}{\micro\metre}$ XXX to be checked XXX yielding a size ratio $q_R=2R_g/\sigma=0.07$. The Brownian time is $\tau_B \approx \SI{4.5}{\second}$. To be able to follow individual trajectories, we perform a 3D scan every \SI{10}{\second} at early time and every \SI{30}{\second} later.

@@

% \paragraph*{Structural analysis}
% To account for imprecision in particle localisation close to contact, we consider two particles bonded if their center-to-center distance is within $\SI{2.3}{\micro\metre}>\sigma+2R_g$.
% 
% To detect percolation, two different methods have been employed. In the first one we detect percolation
% by looking at which frame the cluster size distribution has a more extended power-law decay. In the second technique,
% we simply measure the spatial extent of the largest cluster and consider it percolating when it is comparable to the
% size of the field of view of the microscope. Both methods lead to essentially identical percolation time for each state point.

@@
